\bf ``A p-value of $<$ 0.05 was considered statistically significant'': a content analysis of published statistical methods sections

### 2021-05-25 manuscript/asa_template/asa_template_almostdone.tex
update almostdone pdf and bib files

\if0\blind
{
  \title{\bf An observational study of papers published in \emph{PLOS ONE} and
studies posted to a trial registry.}

  \author{
        Nicole White \thanks{The authors gratefully acknowledge computational resources and services
used in this work provided by the eResearch Office, Queensland
University of Technology, Brisbane, Australia.} \\
    School of Public Health and Social Work, QUT\\
     and \\     Thiru Balasubramaniam, Richi Nayak \\
    To add\\
     and \\     Adrian Barnett \\
    School of Public Health and Social Work, QUT\\
      }
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf An observational study of papers published in \emph{PLOS ONE} and
studies posted to a trial registry.}
  \end{center}
  \medskip
} \fi

@@

A potential contributor to poor statistical reporting is the temptation for researchers to replicate
descriptions of statistical methods, in an effort to make their papers resemble those of their peers 
and increase perceived chances of publication  \citep{Diong2018}. Two statisticians on this paper 
(AB and NW) have heard researchers admit
that they have copied-and-pasted their statistical methods sections from
other papers, regardless of whether they are appropriate. For this paper, we applied a text-based 
clustering method to analyse the content of statistical methods sections included in common scientific research outputs.
Clustering results are then evaluated to estimate the extent that researchers are
using cut-and-paste or `boilerplate' statistical methods sections.
Boilerplate text is that ``which can be reused in new contexts or
applications without significant changes to the original''
\citep{Wikipedia}. Use of these methods sections indicates that little
thought has gone into the statistical analysis.

@@

\emph{PLOS ONE} is a large open access journal that publishes original
research across a wide range of scientific fields. Article submissions
are handled by an academic editor who selects peer reviewers based on
their self-nominated areas of expertise. Submissions do not undergo
formal statistical review. Instead, reviewers are required to assess
submissions against several publication criteria, including whether:
``Experiments, statistics, and other analyses are performed to a high
technical standard and are described in sufficient detail''
\citep{PLOS}. All reviewers are asked the question: ``Has the
statistical analysis been performed appropriately and rigorously?'',
with the possible responses of ``Yes'', ``No'' and ``I don't know''.

@@

Data included in our analysis were downloaded on 3 July 2020. For
records that did not pass Step 2, we reviewed where initial search terms
appeared in the full-text, to determine the proportion of
statistical methods sections that were missed under our chosen approach.

@@

Statistical methods sections were missing for some studies downloaded
from ANZCTR, including a small number of sections labelled as ``Not
applicable'', ``Nil'' or ``None''. We therefore examined if there were
particular studies where this section was more likely to be missing.
Analysis considered a logistic regression model estimated in the
Bayesian framework {[}\citet{INLA}; www.r-inla.org{]}, with missing
statistical methods section (yes/no) as the dependent variable. Date,
study type (observational or interventional), number of funders and
target sample size were used as independent variables. Results were
reported as odds ratios with 95\% credible intervals (CI).

@@

We compiled an extensive list of statistical terms to standardise
reported descriptions of statistical methods. An initial list was
compiled by calculating individual word frequencies and identifying
relevant terms that appeared at least 100 times. Further terms were
sourced from index searches of three statistics textbooks
\citep[\citet{Diggle2013},\citet{Bland2015}]{Dobson2018}. Plurals (e.g.,
`chi-squares') unhyphenated (e.g., `chi square') and combined
(e.g.~`chisquare') terms were transformed to singular, hyphenated form
(e.g., `chi-square'). Common statistical tests were also hyphenated
(e.g., `hosmer lemeshow' to `hosmer-lemeshow'). The final list is
provided in Supplementary File 1.

@@

For \(N\) studies, let \(P \in R^{M \times N}\) denote a content matrix,
representing text from statistical methods sections as \(M\) unique
terms. Text clustering algorithms for identifying common topics across
studies requires \(P\) to be represented with a vector space model. In
our case, unique terms in \(P\) are modelled using the tf*idf (term
frequency \(\times\) inverse document frequency) weighting schema, to
account for the relative importance of common and rare terms.

A common problem facing text clustering algorithms is the curse of
dimensionality due to the high number of terms in the doc\(\times\)term
matrix representation
\citep[\citet{sutanto2018fine}]{aggarwal2012mining}. Applying text-based
methods based on distance, density or probability therefore face
difficulties in high-dimensional settings
\citep[\citet{mohotti2018corpus},\citet{mohotti2019concept}]{park2018examining}.
Specifically, distances between near and far points becomes negligible
\citep{aggarwal2012mining}. This behaviour directly affects the
performance of distance-based clustering methods such as
\textit{k}-means \citep{jain} in accurately identifying subgroups
(topics) present in the data. Furthermore, sparseness associated with
high-dimensional matrix representations does not allow for
differentiation between topics based on density differences
\citep[\citet{mohotti2018efficient}]{mohotti2018corpus}.

@@

Following estimation, \textit{H} contains the information regarding
topic membership for all studies. In our case, topic membership
\((1,\ldots,g)\) for a statistical methods section is inferred from the
maximum coefficient value in the corresponding row of \(H\), also known
as the topic coherence score. For our two datasets, we applied NMF with
\(g=10\).

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{plos-one}{%
\subsection{PLOS ONE}\label{plos-one}}

@@

@@

API searches returned 131,847 results (DOIs)
(\autoref{fig:consort-diagrams}). After partial matching, 111,731 (85\%)
statistical methods sections were identified. In the final sample,
95,518 (85\%) DOIs returned an exact match against common section
headings: 64,133 for `statistical analysis', 13,380 for `statistical
analyses' and 13,627 for `data analysis'.

Search results varied by journal volume (Figure \ref{fig:plos-n}A). The
total number of API search results peaked at volumes 8 (n = 19,045) and
9 (n = 19,045) in years 2013 and 2014. This trend aligned with the total
number of papers published in \emph{PLOS ONE} over the same period. The
percentage of records that included a statistical methods section varied between 64\%
(volume 2) and 86\% (volume 9). All DOIs included Biology and life
sciences (n = 107,584), Earth sciences (n = 7,605) and/or Computer and
information sciences (n = 5,190) in their top 3 subject classifications
(Figure \ref{fig:plos-n}B).

@@

For studies excluded based on section headings, initial search terms
appeared in Introduction (number), Results (number) only. xxx appeared
in the Methods section without a section heading and xxx had a
non-standard section heading. {[}TODO{]}.

@@

\caption{\label{fig:plos-clouds}Topic clouds for ten clusters for PLOS ONE}\label{fig:unnamed-chunk-6}
\end{figure}

The topic clouds for ten clusters are in Figure \ref{fig:plos-clouds}.
Frequently occurring words reflected the use of statistical software
(topics 3 and 5), descriptive statistics (topic 6), group based
hypothesis testing (topics 1 and 4) and definitions of statistical
significance (topics 1 and 9). Topics related to
regression (topic 2) and meta-analysis (topic 7) were also identified.
Examples of boilerplate text for selected topics are presented in Table
\ref{tab:plos-example-boilerplate}.

Topics related to statistical software differentiated between Prism
GraphPad (topic 3: n = 9974; 8.6\%) and SPSS (topic 5: n = 9648; 8.3\%).
Within topic 3, the sentence ``GraphPad Prism (Graphpad Software, San
Diego, CA) was used for all analyses'' was matched in 1,941 studies based on our definition of boilerplate text.
Similarly, for topic 5, ``SPSS software version
17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis'' returned matches for 441 studies.

@@

\caption{\label{tab:plos-example-boilerplate}Example boilerplate text from PLOS ONE datase (sentence level). Statistical methods text corresponds to the DOI with the highest topic coherence score within a topic}
\centering
\begin{tabular}[t]{p{0.1\textwidth}p{0.9\textwidth}p{0.1\textwidth}}
\hline
Topic & Statistical methods text & Matching DOIs\\
\hline
Topic 1 & $^{\dagger}$Students t-test was used for statistical analysis. & 29\\
\cline{2-3}
 & $^{\dagger}$A p value of $<$ 0.05 was considered statistically significant. & 1883\\
\hline
Topic 3 & $^{\dagger}$GraphPad Prism (Graphpad Software, San Diego, CA) was used for all analyses. & 1941\\
\hline
Topic 4 & $^{\dagger}$Significant differences were determined using analysis of variance (ANOVA) followed by tukey post-hoc tests for multiple comparisons. & 2216\\
\hline
Topic 5 & $^{\dagger}$SPSS software version 17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis. & 441\\
\hline
Topic 6 & $^{\dagger}$All results are expressed as means $\pm$ standard deviation ($\pm$ SD). & 102\\
\hline
Topic 9 & $^{\dagger}$Statistical significance was determined by Students t-tests. & 49\\
\cline{2-3}
& $^{\dagger}$ $^*$p $<$ 0.05, $^{**}$p $<$ 0.01, $^{***}$p $<$ 0.001. & 6\\
\hline
\end{tabular}
\end{table}
\end{landscape}

Definitions of statistical significance featured strongly in topic 1 (n
= 3784; 3.2\%) and topic 9 (n = 6195; 5.3\%). Topic 1 reflected
applications of two-tailed and unpaired Student's t-tests, however,
instances of boilerplate text emphasised the 5\% level of statistical
significance (Table \ref{tab:plos-example-boilerplate}). In contrast, Topic 9
focused on multiple thresholds for declaring statistical significance by
asterisk: ``\(^{*}p<0.05\), \(^{**}p<0.01\) and \(^{***}p<0.001\)'', a
practice that has been criticised \citep{Wasserstein2019}.

Group-based hypothesis testing was a recurring theme across topics, with
text descriptions varying based on method(s) used. One-way analysis of
variance also featured strongly in topic 4 (n = 10212; 8.8\%), combined
with common methods for performing post-hoc multiple comparisons. Based
on the Jaccard index, 1 in 5 studies were matched to the sentence
``Significant differences were determined using analysis of variance
(ANOVA) followed by Tukey post-hoc tests for multiple comparisons''.
Frequently occurring words in topic 6 (n = 4764; 4.1\%) reflected
mentions of descriptive statistics for summarising continuous variables,
namely means with standard deviations or standard errors.

@@

Odds ratios and 95\% credible intervals for study characteristics
included in the logistic regression model are presented in Table
\ref{tab:anzctr-missing-odds}. Observational studies were less likely to
have a missing statistical methods section compared with interventional
studies. Missing sections became less likely over time. Studies with
more funders and a larger target sample size were less likely to have a
missing statistical methods section.

@@

\caption{ANZCTR topic clouds.}\label{fig:unnamed-chunk-9}
\end{figure}

The clustering algorithm found groups that were purely sample size
calculations (topic 2, n = 1834), pilot studies (topic 5, n = 834),
safety/tolerability studies (topic 6, n = 524), intervention studies
(topic 8, n = 1020) and repeated measures ANOVA (topic 10 = 852).
Examples of boilerplate text are provided in Table
\ref{tab:anzctr-example-boilerplate} .

Some methods sections were only one word, including ``ANOVA'',
``t-test'', ``SPSS'' and even ``SSPS''. There were cases where the exact
same method section had been re-used in a different study. For example,
in topic 7 (n = 333), 232 sections stated `descriptive statistics' or
`descriptive statistics used' with no additional details provided. Other
instances with expanded descriptions of methods included topic 3 (n =
1277) outlining descriptive analyses only, and topic 6 (n = 524), for
hypothesis testing methods, statistical significance and software.

In other cases, text had been slightly modified to account for changes
in primary and secondary outcomes. Examples of these text changes were
found in topic 2 (n = 1834) and topic 4 (n = 909); identified instances
related to sample size calculations for patient recruitment to different
studies.

Since studies included in this dataset outlined planned analyses, we
hypothesised that some studies did not specify statistical methods because
they had yet to consult with a statistician. Targeted searches for the
term ``statistician'' across all topics returned xx matching records,
with examples including ``A statistician employed by hospital was used''
and ``Pilot study at this point will use a statistician professionally
to determine sample size calculations as required''.

>>>>

\if0\blind
{
  \title{\bf ``A p-value of $<$ 0.05 was considered statistically significant'': a content analysis of published statistical methods sections}

  \author{
        Nicole M White \thanks{The authors gratefully acknowledge computational resources and services
used in this work provided by the eResearch Office, Queensland
University of Technology, Brisbane, Australia.} \\
    \small{Australian Centre for Health Services Innovation and Centre for Healthcare Transformation} \\
\small{School of Public Health and Social Work, Queensland University of Technology} \\
     and \\     Thiru Balasubramaniam, Richi Nayak \\
    \small{Centre for Data Science and School of Computer Science} \\
\small{Queensland University of Technology} \\
     and \\     Adrian G Barnett \\
    \small{Australian Centre for Health Services Innovation and Centre for Healthcare Transformation} \\
\small{School of Public Health and Social Work, Queensland University of Technology} \\
      }
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf ``A p-value of $<$ 0.05 was considered statistically significant'': a textual analysis of published statistical methods sections}
  \end{center}
  \medskip
} \fi

@@

A potential contributor to poor statistical reporting is the temptation for researchers to re-use
descriptions of statistical methods, in an effort to make their papers resemble those of their peers 
and increase perceived chances of publication  \citep{Diong2018}. Two statisticians on this paper 
(AB and NW) have heard researchers admit
that they have copied-and-pasted their statistical methods sections from
other papers, regardless of whether they are appropriate. For this paper, we applied a text-based 
clustering method to analyse the content of published statistical methods sections.
Clustering results are then evaluated to estimate the extent that researchers are
using cut-and-paste or `boilerplate' statistical methods sections.
Boilerplate text is that ``which can be reused in new contexts or
applications without significant changes to the original''
\citep{Wikipedia}. Use of these methods sections indicates that little
thought has gone into the statistical analysis.

@@

\emph{PLOS ONE} is a open access mega-journal that publishes original
research across a wide range of scientific fields. Article submissions
are handled by an academic editor who selects peer reviewers based on
their self-nominated areas of expertise. Currently there are 324 academic editors out of 9,648 (3\%) 
with the keywords of "statistics (mathematics)" or "statistical methods" in their expertise list (web search on 25-May-2021,
 https://journals.plos.org/plosone/static/editorial-board). Submissions do not undergo
formal statistical review. Instead, reviewers are required to assess
submissions against several publication criteria, including whether:
``Experiments, statistics, and other analyses are performed to a high
technical standard and are described in sufficient detail''
\citep{PLOS}. All reviewers are asked the question: ``Has the
statistical analysis been performed appropriately and rigorously?'',
with the possible responses of ``Yes'', ``No'' and ``I don't know''.

@@

Data were downloaded on 3 July 2020. For
records that did not pass Step 2, we reviewed where initial search terms
appeared in the full-text, to determine the proportion of
statistical methods sections that were missed under our chosen approach.

@@

Statistical methods sections were missing for some studies downloaded
from ANZCTR, including sections labelled as ``Not
applicable'', ``Nil'' or ``None''. We examined if there were
particular studies where the statistical methods section was more likely to be missing.
Analysis considered a logistic regression model estimated in the
Bayesian framework {[}\citet{INLA}; www.r-inla.org{]}, with missing
statistical methods section (yes/no) as the dependent variable. The independent variables were date,
study type (observational or interventional), number of funders and
target sample size. Results were
reported as odds ratios with 95\% credible intervals (CI).

@@

We compiled an extensive list of statistical terms to standardise
reported descriptions of statistical methods. An initial list was
compiled by calculating individual word frequencies and identifying
relevant terms that appeared at least 100 times. Further terms were
sourced from index searches of three statistics textbooks
\citep{Diggle2013,Bland2015,Dobson2018}. Plurals (e.g.,
`chi-squares') unhyphenated (e.g., `chi square') and combined
(e.g.~`chisquare') terms were transformed to singular, hyphenated form
(e.g., `chi-square'). Common statistical tests were also hyphenated
(e.g., `hosmer lemeshow' to `hosmer-lemeshow'). The final list is
provided in Supplementary File 1.

@@

For \(N\) studies, let \(P \in R^{M \times N}\) denote a content matrix of text from statistical methods sections as \(M\) unique
terms. Text clustering algorithms for identifying common topics across
studies requires \(P\) to be represented with a vector space model. In
our case, unique terms in \(P\) are modelled using the tf-idf (term
frequency \(\times\) inverse document frequency) weighting schema, to
account for the relative importance of common and rare terms.

A common problem facing text clustering algorithms is the curse of
dimensionality due to the high number of terms in the doc\(\times\)term
matrix representation
\citep[\citet{sutanto2018fine}]{aggarwal2012mining}. Applying text-based
methods based on distance, density or probability therefore face
difficulties in high-dimensional settings
\citep[\citet{mohotti2018corpus},\citet{mohotti2019concept}]{park2018examining}.
Specifically, distances between near and far points becomes negligible
\citep{aggarwal2012mining}. This behaviour directly affects the
performance of distance-based clustering methods such as
\textit{k}-means \citep{jain2010} in accurately identifying subgroups
(topics) present in the data. Furthermore, sparseness associated with
high-dimensional matrix representations does not allow for
differentiation between topics based on density differences
\citep[\citet{mohotti2018efficient}]{mohotti2018corpus}.

@@

Following estimation, \textit{H} contains the information regarding
topic membership for all studies. In our case, topic membership
\((1,\ldots,g)\) for a statistical methods section is inferred from the
maximum coefficient value in the corresponding row of \(H\), also known
as the topic coherence score. For our two datasets, we applied NMF with
\(g=10\) topics.

@@

\clearpage

\section{Results}\label{results}

\subsection{PLOS ONE}\label{plos-one}

API searches returned 131,847 papers (DOIs)
(\autoref{fig:consort-diagrams}). After partial matching, 111,731 (85\%)
statistical methods sections were identified. In the final sample,
95,518 (85\%) DOIs returned an exact match against common section
headings: 64,133 for `statistical analysis', 13,380 for `statistical
analyses' and 13,627 for `data analysis'.

\begin{figure}[htbp]

@@

\begin{figure}[htbp]

@@

Search results varied by journal volume (Figure \ref{fig:plos-n}A). The
total number of API search results peaked at volumes 8 (n = 19,045) and
9 (n = 19,045) in years 2013 and 2014. This trend aligned with the total
number of papers published in \emph{PLOS ONE} over the same period. The
percentage of records that included a statistical methods section varied between 64\%
(volume 2) and 86\% (volume 9). All DOIs included ``Biology and life
sciences'' (n = 107,584), ``Earth sciences'' (n = 7,605) and/or ``Computer and
information sciences'' (n = 5,190) in their top 3 subject classifications
(Figure \ref{fig:plos-n}B).

@@

For studies excluded based on section headings (n = 20,116), analysis-related search terms for 2,136 DOIs appeared in the general text of the Materials and Methods section. For studies without a matching Materials and Methods section,
 search terms oftern appeared in the Introduction (n = 728) and Results and/or Discussion (n = 981) sections. 4,010 DOIs included at least 1 section heading that contained the terms ``analysis'' or ``analyses'' without direct reference to statistical method(s) (e.g. Microarray analysis).

@@

\caption{\label{fig:plos-clouds}Word clouds for ten topics for statistical methods sections published in PLOS ONE}\label{fig:unnamed-chunk-6}
\end{figure}

The word clouds for ten topics are in Figure \ref{fig:plos-clouds}.
Frequently occurring words reflected the use of statistical software
(topics 3 and 5), descriptive statistics (topic 6), group based
hypothesis testing (topics 1 and 4) and definitions of statistical
significance (topics 1 and 9). Topics related to
regression (topic 2) and meta-analysis (topic 7) were also identified.
Examples of boilerplate text for selected topics are in Table
\ref{tab:plos-example-boilerplate}.

Topics related to statistical software differentiated between Prism
GraphPad (topic 3: n = 9974) and SPSS (topic 5: n = 9648).
Within topic 3, the sentence ``GraphPad Prism (Graphpad Software, San
Diego, CA) was used for all analyses'' was matched in 1,941 papers based on our definition of boilerplate text.
Similarly, for topic 5, ``SPSS software version
17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis'' returned matches for 441 papers.

@@

\caption{\label{tab:plos-example-boilerplate}Example boilerplate text from PLOS ONE papers (sentence level). The number of matching to each sentence was based on a Jaccard score of 0.9 or higher and a difference in word count of $\pm$ 3 words}
\centering
\begin{tabular}[t]{p{0.1\textwidth}p{0.9\textwidth}p{0.1\textwidth}}
\hline
Topic & Statistical methods text & Matching papers\\
\hline
Topic 1 & Students t-test was used for statistical analysis. & 29\\
\cline{2-3}
 & A p value of $<$ 0.05 was considered statistically significant. & 1883\\
\hline
Topic 3 & GraphPad Prism (Graphpad Software, San Diego, CA) was used for all analyses. & 1941\\
\hline
Topic 4 & Significant differences were determined using analysis of variance (ANOVA) followed by tukey post-hoc tests for multiple comparisons. & 2216\\
\hline
Topic 5 & SPSS software version 17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis. & 441\\
\hline
Topic 6 & All results are expressed as means $\pm$ standard deviation ($\pm$ SD). & 102\\
\hline
Topic 9 & Statistical significance was determined by Students t-tests. & 49\\
\cline{2-3}
&  $^*$p $<$ 0.05, $^{**}$p $<$ 0.01, $^{***}$p $<$ 0.001. & 6\\
\hline
\end{tabular}
\end{table}
\end{landscape}

Definitions of statistical significance featured strongly in topic 1 (n
= 3784) and topic 9 (n = 6195). Topic 1 reflected
applications of two-tailed and unpaired Student's t-tests, however,
instances of boilerplate text emphasised the 5\% level of statistical
significance (Table \ref{tab:plos-example-boilerplate}). In contrast, Topic 9
focused on multiple thresholds for declaring statistical significance by
asterisk: ``\(^{*}p<0.05\), \(^{**}p<0.01\) and \(^{***}p<0.001\)'', a
practice that has been criticised \citep{Wasserstein2019}.

Group-based hypothesis testing was a recurring theme across topics, with
text descriptions varying based on method(s) used. One-way analysis of
variance also featured strongly in topic 4 (n = 10212), combined
with common methods for performing post-hoc multiple comparisons. Based
on the Jaccard index, 1 in 5 studies were matched to the sentence
``Significant differences were determined using analysis of variance
(ANOVA) followed by Tukey post-hoc tests for multiple comparisons''.
Frequently occurring words in topic 6 (n = 4764) reflected
mentions of descriptive statistics for summarising continuous variables,
namely means with standard deviations or standard errors.

@@

Odds ratios and 95\% credible intervals for study characteristics
associated with missing statistical methods sections are in Table
\ref{tab:anzctr-missing-odds}. Observational studies were less likely to
have a missing statistical methods section compared with interventional
studies. Missing sections became less likely over time. Studies with
more funders and a larger target sample size were less likely to have a
missing statistical methods section.

@@

\caption{Word clouds for ten topics for statistical methods sections published in ANZCTR}\label{fig:unnamed-chunk-9}
\end{figure}

The text clustering algorithm found topics that were purely sample size
calculations (topic 2, n = 1834), pilot studies (topic 5, n = 834),
safety/tolerability studies (topic 6, n = 524), intervention studies
(topic 8, n = 1020) and repeated measures ANOVA (topic 10 = 852).
Examples of boilerplate text are provided in Table
\ref{tab:anzctr-example-boilerplate} .

Some methods sections were only one word, including ``ANOVA'',
``t-test'', ``SPSS'' and even ``SSPS''. There were cases where the exact
same method section had been re-used in a different study. For example,
in topic 7 (n = 333), 232 sections stated `descriptive statistics' or
`descriptive statistics used' with no additional details provided. Other
instances with expanded descriptions of methods included topic 3 (n =
1277) outlining descriptive analyses only, and topic 6 (n = 524), for
hypothesis testing methods, statistical significance and software. 
In other cases, text had been slightly modified to account for changes
in primary and secondary outcomes. Examples of these text changes were
found in topics 2 and 4; identified instances
related to sample size calculations for patient recruitment to different
studies.

Since studies in this dataset described planned analyses, we
hypothesised that some studies did not specify statistical methods because
they had yet to consult with a statistician. Targeted searches for ``statistician'' across all topics returned 1,277 matching studies,
with examples including ``A statistician employed by hospital was used''
and ``Pilot study at this point will use a statistician professionally
to determine sample size calculations as required''.
